APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
mention of ensemble methods no longer needed
formalize model selection and copyedit

where $\mathcal{H}$ is the set of all possible \textit{hyperparameter} settings
for the estimator in question.\footnote{
  We disregard the fact that different estimators
  have widely varying sets of hyperparameters for notational simplicity.}
Hyperparameters include, for example,
regularization strength of linear models or SVMs,
choice of loss function for generic linear model learners,
or the number of features to keep in a feature selection method.
They are often treated as user-settable parameters
and not part of the learning problem proper,
either because they would affect the learning problem
in a way that would make it intractable \citep{bergstra2012}
or because their effects cannot properly be measured
in terms of a loss function on a training set.

However, in recent years, algorithms have been published
that systematically explore spaces of possible hyperparameter settings.
The problem of hyperparameter tuning
is crucial to achieving good generalization performance in machine learning.
The present paper does not go into hyperparameter optimization algorithms
in depth, focusing instead on API support for using them.

@@

By composing, say, a \texttt{CountVectorizer} object
(which extracts term frequency features from text documents
according to a bag-words model),
a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
one obtains a pipeline object with various hyperparameters:
whether to do stopword filtering,
linear vs.\ logarithmic \textsf{tf}, number of features to keep,
SVM regularization ($L_1$ or $L_2$ norm, strength $C$) a.o.
Such a composite \texttt{Pipeline} object
exposes all of these parameters using a special syntax;
each estimators must be given a name,
and if the SVM's name is, e.g., \texttt{linearsvm},
then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.
The pipeline's \texttt{set\_params} splits the parameter names
on double underscores, uses the first part of the result
to look up the estimator,
and passes the second part to the estimator's own \texttt{set\_params}
as a keyword argument; due to Python's dynamic parameter passing,
the result is the same as if the user had called \texttt{set\_params}
on the SVM themselves.
(The double underscore syntax is not special to pipelines;
it is also employed in ensemble estimators such as random forests.)

>>>>

Here, $\mathcal{H}$ is the set of all possible \textit{hyperparameter} settings
for the estimator in question.\footnote{
  We disregard the fact that different estimators
  have widely varying sets of hyperparameters for notational simplicity.}
Hyperparameters include, for example,
regularization strength of linear models or SVMs,
choice of loss function for generic linear model learners,
or the number of features to keep in a feature selection method.
They are often treated as user-settable parameters
and not part of the learning problem proper,
either because they would affect the learning problem
in a way that would make it intractable \citep{bergstra2012}
or because their effects cannot properly be measured
in terms of a loss function on a training set.

However, in recent years, algorithms have been published
that systematically explore spaces of possible hyperparameter settings,
a problem that can be formalized as learning and optimization
within the set of subset of hyperparameter space:

\[
  L' : 2^\mathcal{H} \to \mathcal{X} \to \mathcal{Y}
\]

The problem of hyperparameter tuning
is crucial to achieving good generalization performance in machine learning.
The present paper does not go into hyperparameter optimization algorithms
in depth, but instead focuses on the design of an API
that facilitates the use of such algorithms.

@@

By composing, say, a \texttt{CountVectorizer} object
(which extracts term frequency features from text documents
according to a bag-words model),
a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
one obtains a pipeline object with various hyperparameters:
whether to do stopword filtering,
linear vs.\ logarithmic \textsf{tf}, number of features to keep,
SVM regularization ($L_1$ or $L_2$ norm, strength $C$) a.o.
Such a composite \texttt{Pipeline} object
exposes all of these parameters using a special syntax;
each estimators must be given a name,
and if the SVM's name is, e.g., \texttt{linearsvm},
then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.
The pipeline's \texttt{set\_params} splits the parameter names
on double underscores, uses the first part of the result
to look up the estimator,
and passes the second part to the estimator's own \texttt{set\_params}
as a keyword argument; due to Python's dynamic parameter passing,
the result is the same as if the user had called \texttt{set\_params}
on the SVM themselves.
